Nested sampling with two objective functions

### 2015-11-29 Paper/ms.tex

@@

Here we describe the proposed algorithm, which took three years of
experimentation to develop. Please contact the first author for a list of
failed ideas, some of which might lead to potential alternatives to this
algorithm.

\begin{algorithm}
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
$N$ should be odd and quite large (1001 or greater).
\State Initialise the {\em remaining prior mass} to be $M=1$.
\State Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
$\emptyset$.
\While{more iterations desired}
	\State Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
			and sort the $\hat{X}$ values observed.
	\State Find the median $\hat{X}$ value, $\hat{X}_{(k)}$, where $k = (N-1)/2$.
	\While{$k > 1$ and $\hat{X}_{(k-1)} = \hat{X}_{(k)}$}
		\State Set $k \leftarrow (k-1)$.
	\EndWhile
	\State Save all particles with $\hat{X} \geq \hat{X}_{(k)}$ to disk,
			assigning each a prior weight of $M/N$.
	\State Exclude the region in the $L_1$-$L_2$ plane where
$\hat{X} \geq \hat{X}_{(k)}$. That is, set
	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
	\State Update the remaining prior mass to $M \leftarrow M(1 - k/N)$.
	\State Replace all particles with $\hat{X} \geq \hat{X}_{(k)}$ by new
			particles generated from $\pi(\xx)$, subject to the constraint
			of not being in the excluded region.
\EndWhile
\end{algorithmic}
\end{algorithm}

Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.

>>>>

\section{Rationale}\label{sec:rationale}

{\bf Here is where I'll attempt to provide a justify the
algorithm}.

@@

The proposed algorithm is given in Algorithm~\ref{alg:algorithm}
and took three years of
experimentation to develop. Please contact the first author for a list of
failed ideas, some of which might lead to potential alternatives to this
algorithm. The basic idea is to try to mimic a standard NS run, where the
objective function being increased is
\begin{eqnarray}
Y(\xx) &=& -\ln\left[X\left(L_1(\xx), L_2(\xx)\right)\right].
\end{eqnarray}

\begin{algorithm}[ht!]
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
$N$ should be odd and quite large (1001 or greater).
\State Initialise the {\em remaining prior mass} to be $M=1$.
\State Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
$\emptyset$.
\While{more iterations desired}
	\State Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
			and sort the $\hat{X}$ values observed.
	\State Find the median $\hat{X}$ value, $\hat{X}_{(k)}$, where $k = (N-1)/2$.
	\While{$k > 1$ and $\hat{X}_{(k-1)} = \hat{X}_{(k)}$}
		\State Set $k \leftarrow (k-1)$.
	\EndWhile
	\State Save all particles with $\hat{X} \geq \hat{X}_{(k)}$ to disk,
			assigning each a prior weight of $M/N$.
	\State Exclude the region in the $L_1$-$L_2$ plane where
$\hat{X} \geq \hat{X}_{(k)}$. That is, set
	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
	\State Update the remaining prior mass to $M \leftarrow M(1 - k/N)$.
	\State Replace all particles with $\hat{X} \geq \hat{X}_{(k)}$ by new
			particles generated from $\pi(\xx)$, subject to the constraint
			of not being in the excluded region.
\EndWhile
\end{algorithmic}
\caption{\label{alg:algorithm}}
\end{algorithm}

%Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.
